Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-07-27 ms.tex
correctly accounted for all barycentric and systematic velocity offsets in all plots.

The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
High precision radial velocity measurements of the host star with Keck/HIRES put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
\citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 m/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the \kepler\ bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$ (determined by the mass of dust needed to absorb and scatter 10$^{-2}$ of star light per orbit), the modeled mass is 0.014 $M_\oplus$ \citep{perez-becker}.

@@

\subsection{Data Reduction}
For the 2015 data, we use the same spectra, as in \citet{masuda2018rvKIC1255}.
All telluric emission features and outliers are masked in this analysis to remove these components.
Time-variable outliers, such as cosmic rays, are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
We combined the normalized spectra from UT dates 2015 Aug 28 and 2015 Aug 29 with a median in the time direction, which is more robust to cosmic rays than an average.
%This median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.

>>>>

The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
High precision radial velocity measurements of the host star with Keck/HIRES put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
\citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 m/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the \kepler\ bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$ (determined by the mass of dust needed to absorb and scatter 10$^{-2}$ of star light per orbit), the modeled mass is 0.014~$M_\oplus$ \citep{perez-becker}.

@@

\subsection{Data Reduction}
For the 2015 data, we use the same spectra, as in \citet{masuda2018rvKIC1255}.
All telluric emission features and outliers are masked in this analysis to remove these components.
Time-variable outliers, such as cosmic rays, are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
The wavelength of each spectrum is shifted to correct for the observatory's motion about the Solar Systems barycenter as well as the systematic -36.3 km/s velocity \citep{croll2014}.
We combined the normalized spectra from UT dates 2015 Aug 28 and 2015 Aug 29 with a median in the time direction, which is more robust to cosmic rays than an average.
%This median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.
